\added{GrapeCPNet: A Self-supervised Point Cloud Completion Network for 3D Phenotyping of Grape Bunches}

### 2025-02-17 main.tex
decrease references

% challenges, limitations and future works.
\added{Another limitation of this study is that it focused on a single berry bunch in a controlled environment.}
The noise in the data is also related to the effectiveness of the method proposed in this paper.
\added{For practical applications in vineyards, collecting the same point cloud quality as that achieved in controlled indoor environments can be challenging, and multi-view data collection may not be as efficient.}
How to \added{effectively} implement the method in practical application scenarios\deleted{, such as RGB-D collected point cloud data,} is another issue to be considered in future research.
\added{To increasing data collection efficiency, devices such as RGB-D cameras \citep{blok_highthroughput_2025}, fisheye cameras \citep{tamura_unsupervised_2025}, or even 360 cameras can be used.}
\added{Moreover, as in previous studies \citep{rose_automated_2016, luo_3d_2023}, investigating methods to segment individual grape bunches directly from vineyard scans using deep learning techniques should be an area of future exploration.}
\added{Additionally, \citet[Fig.~9]{scholer_automated_2015} successfully demonstrated the construction of virtual 3D models of grape bunches, including the hidden branching architecture. }
\added{By collecting time-series growth data, the branching structure could potentially be captured during early stages of thinning, as suggested by \citep{du_instance_2023}.}
\added{Such data could enable studies on growth prediction for optimizing harvesting times and assessments of branching structure deviations within crowded berry bunches.}
\added{Finally, applying the latest procedural computer graphics (CG) modeling techniques \citep{karoly_automated_2022} or functional-structural plant models \citep{helmrich_scalable_2024} represents another promising approach to advancing practical applications in this field.}

>>>>

% challenges, limitations and future works.
\added{Another limitation of this study is that it focused on a single berry bunch in a controlled environment.}
The noise in the data is also related to the effectiveness of the method proposed in this paper.
\added{For practical applications in vineyards, collecting the same point cloud quality as that achieved in controlled indoor environments can be challenging, and multi-view data collection may not be as efficient.}
How to \added{effectively} implement the method in practical application scenarios\deleted{, such as RGB-D collected point cloud data,} is another issue to be considered in future research.
\added{To increasing data collection efficiency, devices such as RGB-D cameras \citep{blok_highthroughput_2025}, fisheye cameras \citep{tamura_unsupervised_2025}, or even 360 cameras can be used.}
\added{Moreover, as in previous studies \citep{rose_automated_2016, luo_3d_2023}, investigating methods to segment individual grape bunches directly from vineyard scans using deep learning techniques should be an area of future exploration.}
\added{Additionally, \citet[Fig.~9]{scholer_automated_2015} successfully demonstrated the construction of virtual 3D models of grape bunches, including the hidden branching architecture. }
\added{By collecting time-series growth data, the branching structure could potentially be captured during early stages of thinning, as suggested by \citep{du_instance_2023}.}
\added{Such data could enable studies on growth prediction for optimizing harvesting times and assessments of branching structure deviations within crowded berry bunches.}
\added{Finally, applying the latest procedural computer graphics (CG) modeling techniques or functional-structural plant models represents another promising approach to advancing practical applications in this field.}
